### 2017-03-10 Manuscripts/model-descriptions/copy-and-tweak/copy-and-tweak.tex
drafted ward copytweak latex

This model assumed that people represent categories as a collection of stored observations. When prompted to generate new examples, they copy and randomly tweak one of the stored examples. Thus, the model's generation is a two-part process:

@@

More formally, let $x$ be a $j$-exemplar by $k$-feature matrix, corresponding to every stored exemplar. The probability that a source example $z$ is selected is given by:

\begin{equation}
  p(z) = exp(f_j) / \sum_j{ exp(f_j) }
\end{equation}

$f_j$ is a vector of values specifying each item's relative chance of being selected. In theory, $f_j$ may be set arbitrarily, but in practice it is sensible to differentiate between members of the target and contrast categories. For example, $f_j = -\gamma$ for members of contrast categories, and $f_j = \gamma$ for members of the target category. The resulting free parameter $\gamma$ ($>0$) thus controls the degree favoritism for members of the target category, with larger values producing larger differentials.

After a source exemplar $z$ is selected, similarity between candidate generation options $y$ is computed:

@@

Where $c$ and $w_k$ are the standard specificity and attention weights discussed elsewhere. The probability a candidate stimulus will be generated is given by:

\begin{equation}
  p(y|z) \propto  
  \begin{cases}
     exp(\theta s(y,z)), & \text{if } s(y,z) \leq \phi \\
    0, & \text{otherwise}
  \end{cases}
  \label{eq:generation-choice}
\end{equation}

where $\theta$ is a response determinism parameter. $\phi$ is a similarity tolerance parameter ($0 \leq \phi \leq 1$) specifying the amount of dissimilarity tolerated between $y$ and $z$. Larger values allow for more similar examples to be generated. The final choice is made using a normalization of all possible values of $p(y|z)$.

\subsection*{The Practical Implementation}

In practice, however, it is useful to be able to generate model predictions more deterministically (i.e., without respect to any given source exemplar $z$). Generalizing things a little, the overall probability that an item $y$ will be generated is the sum of its generation probabilities given every possible source example $z$, $p(y|z)$, weighted by the probability each source will be selected, $p(z)$:

@@

In this way, source-independent probabilities can be obtained without monte-carlo simulation. First, the probability of each source $p(z)$ is computed (which is also required for simulation). Then, the pairwise similarity $s(y,z)$ between each source and each generation candidate is computed. Then the generation probability $p(y|z)$ is computed as per Equation \ref{eq:generation-choice}.  Then $p(y)$ is computed as above.

>>>>

This model assumes that people represent categories as a collection of stored observations. When prompted to generate new examples, they copy and randomly tweak one of the stored examples. Thus, the model's generation is a two-part process:

@@

More formally, let $x$ be a $j$-exemplar by $k$-feature matrix, corresponding to the stored exemplars associated with the target category. The probability that a source example $z$ is selected is uniform across all exemplars. After a source exemplar $z$ is selected, similarity between candidate generation options $y$ is computed:

@@

Where $c$ and $w_k$ are the standard specificity and attention weights discussed elsewhere. The goal of the model is to generate an item that is similar but sufficiently tweaked from the source. Thus, probability a candidate stimulus will be generated is given by:

\begin{equation}
    p(y|z)  = \dfrac
    { \exp \left\{\theta \cdot s(y,z) \right\} I\left(s(y,z) \leq \tau\right) }
    {\sum_i{\exp \left\{ \theta \cdot s(y_i,z) \right\} I\left(s(y_i,z) \leq \tau\right)}} 
    \label{eq:generation-choice}
\end{equation}
% 
where $\theta$ is a response determinism parameter, $\tau$ is the similarity threshold, and $I(\cdot)$ is the indicator function, which returns 1 when it is passed a true expression and 0 otherwise. So, $I\left(s(y,z) \leq \tau\right)$ is 1 when the candidate exemplar $y$ is tweaked enough. When $\tau=1$, the threshold has no effect.

To obtain predictions not depending on a given source example, the model's predictions can be aggregated over all possible sources:

@@
